---
title: "The Chicken Group"
author: "Nitesh"
date: "07/10/2019"
output:
  word_document: default
  pdf_document: default
---
Load Libraries
```{r}
#devtools::install_github("JBGruber/rwhatsapp")
library(rwhatsapp)
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidytext)
library(tidyr)
library(stopwords)
```
Importing files

```{r}
chat <- rwa_read("Chicken_data.txt")
chat <- na.omit(chat)
levels(chat$author) <- c("Nitesh","Dusty","Kshitij","Kshitij","Nitesh","Paresh","Rajat","Tanwir")
head(chat)
```

**Lets first check the number of chit-chats in a day**

```{r}
chat %>%
  mutate(day=date(time)) %>%
  count(day) %>%
  ggplot(aes(x=day,y=n))+geom_bar(stat="identity")+
  ylab("Number of msgs")+xlab("time")+
  ggtitle("Msgs per day")

```

**umm chats have reached till 600 lets first see who is responsible of these talks ..also after 07/2018 we talked less until the placement season XD.**

**If you can find more information you are welcome **

Lets see total texts by person

```{r}
chat %>%
  mutate(day=date(time)) %>%
  count(author) %>%
  ggplot(aes(x=reorder(author,n),y=n,fill=rainbow(6)))+
  geom_bar(stat="identity",col="black")+
  ylab("No of msges")+xlab("Person")+
  coord_flip() + ggtitle("Msg per Person") + theme(legend.position = "none")+
  geom_text(aes(label = scales::comma(n)),hjust=2)
```

**Now we know who talks more** 
**Now its time to watch poeple fav emoji**
```{r}
chat %>%
  unnest(emoji) %>%
  count(author,emoji,sort=T) %>%
  group_by(author)%>%
  top_n(n=6,n)%>%
  ggplot(aes(x=reorder(emoji,n),y=n,fill=author))+
  geom_col(show.legend = F,col="black")+
  ylab("")+xlab("")+coord_flip()+
  facet_wrap(~author,ncol=2,scales="free_y")+
  ggtitle("Most emoji used")

```

**You can judge personalities here .....**
**only i kiss here looks like I M GAY**
**Okay lets look at favorate words to determine**

```{r}
chat %>%
  unnest_tokens(input=text,output=word) %>%
    count(author,word,sort=T)%>%
  filter(nchar(word)>5) %>%
  group_by(author) %>%
  top_n(n=6,n) %>%
  ggplot(aes(x=reorder(word,n),y=n,fill=author))+
  geom_col(show.legend = F)+
  ylab("")+xlab("")+ggtitle("fav words")+
  coord_flip()+facet_wrap(~author,ncol=2,scales="free_y")

```

**Now i have a list of poeple who call each other .Also we share a lot of confidential documents**
Me dushyant and tanwir are good with youtube <3
rajat has "chutiya" in his vocab god bless
Dushyant Likes tanwir;it has high frequency

**Getting owrds that are diffrent for each other will be of more value**
```{r}
to_remove <- c(stopwords("english"),"omitted","message","delete","media","nahi")
chat %>%
  unnest_tokens(input=text,output=word)%>%
  select(word,author) %>%
  filter(nchar(word)>4) %>%
  filter(!word %in% to_remove) %>%
  mutate(word=gsub(".com","",word))%>%
    count(author,word,sort=T) %>%
  bind_tf_idf(term=word,document=author,n=n)%>%
  filter(n>7)%>%
  group_by(author)%>%
  top_n(n=6,tf_idf)%>%
  ggplot(aes(x=reorder(word,n),y=n,fill=author))+
  geom_col(show.legend = F,col="black")+xlab("")+ylab("")+
  coord_flip()+ggtitle("Important Words")+
  facet_wrap(~author,ncol=2,scales="free_y")
```

**Tanwir and kshitj use less slangs**
**Paresh is from delhi**
**dushant is frequent with saala**
**Nitesh is using ayega ya nahi ayega**

**Now lets check who uses more unique words**
```{r}
chat %>%
  unnest_tokens(input=text,output=word)%>%
  filter(!word %in% to_remove) %>%
  group_by(author)%>%
  summarise(lex_diversity=n_distinct(word))%>%
  arrange(desc(lex_diversity))%>%
  ggplot(aes(x=reorder(author,lex_diversity),y=lex_diversity,fill=author)) + geom_col(show.legend = F,col="black")+
           xlab("")+ylab("Unique_words")+
  scale_y_continuous(expand=(multi = c(0,0,0,500)))+
  coord_flip()+ggtitle("Lex-Diversity")+
  geom_text(aes(label = scales::comma(lex_diversity)), hjust = -0.1)
           
```

**Paresh was low on total word than kshitij,but he has vocab**
**Also my total count and vocab was good ,respect me bitches**

**Any more suggestion of insights are welcome if you can find them**


**I dont work for free**




